HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
this fig should have been removed
heatmaps
further on iaa

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
%BH: Not compiling for me, commented out
  \begin{tikzpicture}
    [level 1/.style={sibling distance=7.5em},
      level 2/.style={sibling distance=5em},
      level 3/.style={sibling distance=5em},
      level 4/.style={sibling distance=3em}]
    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [label={B}] [fill=blue, circle] {}
  child {node (H3) [label={A}] [fill=yellow,circle] {}
    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
    child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
      child {node [label={}] {became} edge from parent node[left]  {}}
      child {node [label={}] {a} edge from parent node[left]  {}}
      child {node [label={}] {passion} edge from parent node[left]  {}}
    }
    child {node (H2) [label={A}] [fill=yellow,circle] {}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
      child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
    }
  }
  child {node {} edge from parent[draw=none] {}}
  child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
    child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
  }
  child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
  child {node (H5) [label={A}] [fill=yellow,circle] {}  
    child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
    child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
  };
  \draw[dashed] (H5) -> (she) ;

  \com{
  child {node (H1) [label={\#8}] [fill=black,circle] {}
    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2) [label={\#9}] [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
      child {node [label={\#10}] [fill=black,circle] {}
        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
    }
  \end{tikzpicture}
  \end{adjustbox}
\caption{\label{fig:ucca_example2}
  Sample UCCA annotation. Edge labels mark UCCA categories. \#$<$index$>$ marks the node
indices.}
\end{figure*}

@@

@@

>>>>

@@

\def\iaafig #1{\includegraphics[width=7cm]{iaa_heatmap_#1.png}}

}
\end{tabular}
\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
\label{fig:heatmap}
\end{figure*}

@@

\begin{compactitem}
  \item German has low overall proportion of orange annotation (1.2\% compared with 4.5-8.6)
  \item German annotators give a lot of green (so skewed classes, high expected agreement), but 
        differ more significantly on what should be green. 
  \item For Polish, big difference in number of As (2000 vs 1500) given by each annotator
  \item For Czech structural, both annotators give higher proportion of As, raising the expected agreement.
\end{compactitem}
